Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to validate \textcolor{red}{complex systems}. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. \textcolor{red}{Therefore the focus is in the solar photovoltaic project validation, as intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior. Case studies, ranging from 253 W to 814 W}, were used to evaluate this proposed approach and to compare that with specialized simulation tool. Different verification tools were evaluated as well, in order to compare performance and soundness among automated tools. \textcolor{red}{The results reported by the automated verification and by the simulation tools were compared with data collected from dwellers of the deployed cases, showing the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.}
\end{abstract}

\begin{keyword}
Formal verification \sep model checking \sep photovoltaic power systems
%\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
%\MSC[2010] 00-01\sep  99-00
\end{keyword}

>>>>

\begin{abstract}
\textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic (PV) systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space. Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load. Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying the equipment and deploying it in the field, as a safe approach to ensure the intended behavior. Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated to compare performance and soundness among automated verifiers. The experimental results reported by our automated verification method and by the simulation tools were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
\end{abstract}

\begin{keyword}
Formal verification \sep model checking \sep photovoltaic power systems.
%\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
%\MSC[2010] 00-01\sep  99-00
\end{keyword}
